```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(viridis)
library(here)
library(maps)
library(sf)

states_map <- 
  map_data("state") |> 
  left_join(read_csv(here("data/state_medians.csv")))

plot_temps <- function(palette = c("magma",
                                   "inferno",
                                   "plasma", 
                                   "viridis", 
                                   "cividis", 
                                   "rocket", 
                                   "mako", 
                                   "turbo"),
                       title = TRUE) {
  
  palette_code <- case_match(
    str_to_lower(palette),
    "magma"   ~ "A",
    "inferno" ~ "B",
    "plasma"  ~ "C",
    "viridis" ~ "D",
    "cividis" ~ "E",
    "rocket"  ~ "F",
    "mako"    ~ "G",
    "turbo"   ~ "H"
  )
  
  states_map |>  
    ggplot(aes(x = long, y = lat, fill = med_high, group = group)) +
    geom_polygon(color = "white", linewidth = 0.3) +
    scale_fill_viridis(option = palette_code) +
    coord_sf(
      crs = 5070, default_crs = 4326,
      xlim = c(-125, -70), ylim = c(25, 52)
    ) +
    theme_void() +
    labs(
      title = if_else(
        title, 
        str_to_title(palette), 
        "Median high temperature (F)"
      ),
      fill = ""
    )
}

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("magma")
plot_temps("inferno")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("plasma")
plot_temps("viridis")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("cividis")
plot_temps("rocket")
```

```{r fig.show="hold", fig.width = 5, out.width="50%"}
plot_temps("mako")
plot_temps("turbo")
```

```{r eval = FALSE, echo = TRUE}
mpg |>  
  ggplot(aes(x = displ, y = cty, color = hwy)) +
    geom_point() +
    scale_color_viridis(option = "A")
```
